MSDS6372Project2

### 2021-03-23 MSDS6372Project2.Rmd
minor adjustment

#### Overlay multiple ROC curve together
```{r}
plot(roc.sm1)
plot(roc.complex2,col="orange", add = TRUE)
plot(roc.lda,col="blue",add=TRUE)
plot(roc.rf,col="green",add=TRUE)
legend("bottomright",legend=c("Simple LR","Complex LG","LDA","Random Forest"),col=c("black","orange","blue","green"),lty=1,lwd=1)
abline(a=0, b= 1)

>>>>

#### Overlay multiple ROC curve together
```{r}
plot(roc.sm1)
plot(roc.complex2,col="orange", add = TRUE)
plot(roc.lda,col="blue",add=TRUE)
plot(roc.rf,col="green",add=TRUE)
legend("bottomright",legend=c("Simple LR","Complex LR","LDA","Random Forest"),col=c("black","orange","blue","green"),lty=1,lwd=1)
abline(a=0, b= 1)
